### 2018-03-02 DASFAA_2018/CR/Gruba_final/01-intro.tex

\par Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, has attracted  massive users~\cite{DBLP:journals/fcsc/MaLHLH16,DBLP:journals/tkde/DuanMAMH17,DBLP:conf/icde/HuAMH16,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
These users behave variously, knowledge of whom is significant for various applications such as recommendation system and activity analysis.
Hence there is an emergent demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry~\cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:conf/cikm/JiangLSW15,IEEEexample:conf/sigir/JiangLSLLMW16,IEEEexample:zhang2015retweet,IEEEexample:conf/pakdd/GiatsoglouCSFV15,IEEEexample:journals/corr/RanganathMHTL15}

@@

The key driver of our work is the observation that in social media applications, users could fall into groups and each group shares representative behaviors.
%
As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics.
Particularly, we study the \retg{} behavior of users and our work can be readily generalized to other behaviors of like and comment as well.
In the realm of social network behavior modeling, few work has been done over grouping, which however has been proved to be effective in other fields such as economic behavior analysis.
This motivates us to incorporate user grouping into the \retg{} behavior modeling, filling the gap of existed studies that build a single model for all users.

>>>>

\par Social media is overwhelming nowadays, and popular social networks, e.g., Facebook, Twitter and Weibo, have attracted  massive users~\cite{DBLP:journals/fcsc/MaLHLH16,DBLP:journals/tkde/DuanMAMH17,DBLP:conf/icde/HuAMH16,IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13}.
These users behave variously, knowledge of whom is significant for various applications such as recommendation system and activity analysis.
Hence there is an emergent demand of developing systems and algorithms that could properly model user behaviors, which has already attracted the attention from both academia and industry~\cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:conf/cikm/JiangLSW15,IEEEexample:conf/sigir/JiangLSLLMW16,IEEEexample:zhang2015retweet,IEEEexample:conf/pakdd/GiatsoglouCSFV15,IEEEexample:journals/corr/RanganathMHTL15}

@@

The key driver of our work is the observation that in social media applications, users could fall into groups and each group shares representative behaviors.
%
As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics.
Particularly, we study the \retg{} behavior of users and our work can be readily generalized to other behaviors of ``likes'' and ``comments'' as well.
In the realm of social network behavior modeling, few work has been done over grouping, which however has been proved to be effective in other fields such as economic behavior analysis.
This motivates us to incorporate user grouping into the \retg{} behavior modeling, filling the gap of existing studies that build a single model for all users.

### 2018-03-02 DASFAA_2018/CR/Gruba_final/02-overview.tex

\par We consider the \retg{} behavior of users in social media.
%For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
For simplicity, assuming the microblogs that a user can \ret{} come from those owned by his/her followees.

@@

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message content $M$, and $flag$ denoting $M_b$ is \retd{} or originally \tw{} by $O$. Here we use 1 and 0 to denote \retd{} and  \tw{}, respectively.
\end{definition}

>>>>

\par We consider the \retg{} behavior of users in social media.
%For simplicity, with a given user, we assume that microblogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
For simplicity, assuming the microblogs that a user can \ret{} come from those owned by her/his followees.

@@

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message content $M$, and $flag$ denoting $M_b$ is \retd{} or originally \twd{} by $O$. Here we use 1 and 0 to denote \retd{} and  \tw{}, respectively.
\end{definition}

### 2018-03-02 DASFAA_2018/CR/Gruba_final/03-fe.tex

If $sim(b, \gamma)$ satisfies a certain threshold (3 by default), topic $\gamma$ is labeled to microblog $b$;
the user $u$ is then discovered having an explicit interest (topic $\gamma$).
Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ is derived, in the form of interest feature (see Definition \ref{def:inte}).

@@

To compute such weight $p_i$ for word $w_i$, a metric $p''_i$ is first calculated as:
\begin{equation}
\label{eq:tf-w}
p''_i = \frac{|b_i|}{|b|} * \log(\frac{|D|}{|D_i|+1}),
\end{equation}
in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in microblog $b$, and $|b|$ the total occurrences of all words in $b$.
$|D|$ is the total number of microblogs in the dataset and $|D_i|$ is the number of microblogs where $w_i$ appears.
Hence, each word $w_i$ shall get an initial weight of $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight}.

@@

\etitle{Step 3.2:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained by using Twitter-LDA  %\ref{IEEEexample:zhao2011comparing}
to result the word weight distribution of microblog $b$.
Unlike TF-IDF, Twitter-LDA first trains the overall microblogs, allocating each microblog with a \textit{tag}.
%
The structure of \textit{tag} is as follows:
\begin{equation}
\label{eq:tw-tag}
W_t = \{(w'_i, p'_i)\},
\end{equation}
where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in microblogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$ ($|W_t|\ =\ 30$ in this work by default).
%
Subsequently, $W_t$ are leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.

@@

\stitle{Step 5:} Repeat Steps 1 to 4 for the microblog $b$ over every topic in lexicon, i.e., $\forall {\gamma}_k \in L$ results one similarity value of $sim(b, {\gamma}_k)$.
Such computation further extends to all the microblogs owned by user $u$, such that:
$\forall b_m \in B_s(u)$, $\forall {\gamma}_k \in L$, there exists a similarity of $sim(b_m, {\gamma}_k)$.
Hence, the overall similarity of user $u$ over lexicon topics $\{\gamma\}$ (i.e., $L$), written as $S(u,\ L)$, could be denoted by a vector:
\begin{equation}
\label{eq:simul}
S(u, L) = (s_0, s_1, \ldots,\ s_{n-1}),
\end{equation}
where $n$ refers to the cardinality of $L$ (i.e., number of topics in $L$) and $s_k$ is the overall similarity of user $u$ over topic ${\gamma}_k$, which is given by:
\begin{equation}
\label{eq:simul-2}
s_k = \sum_{\substack{m}} sim(b_m, {\gamma}_k).
\end{equation}

>>>>

If $sim(b, \gamma)$ satisfies a certain threshold (3 by default), topic $\gamma$ is labeled to microblog $b$;
the user $u$ is then discovered having an explicit interest (topic $\gamma$).
Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ are derived, in the form of interest feature (see Definition \ref{def:inte}).

@@

To compute such weight $p_i$ for word $w_i$, a metric $p''_i$ is first calculated as:
\begin{equation}
\label{eq:tf-w}
p''_i = \frac{|b_i|}{|b|} * \log(\frac{|D|}{|D_i|+1}),
\end{equation}
in which we use the operator $|\ |$ to measure the cardinality, such that $|b_i|$ is the occurrences of word $w_i$ in microblog $b$, and $|b|$ the total occurrences of all words in $b$.
$|D|$ is the total number of microblogs in the dataset and $|D_i|$ is the number of microblogs where $w_i$ appears.
Hence, each word $w_i$ shall get an initial weight $p''_i$, upon which the normalization is performed and $p_i$ is obtained, resulting the \textit{TF-IDF weight}.

@@

\etitle{Step 3.2:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained by using Twitter-LDA  %\ref{IEEEexample:zhao2011comparing}
to result the word weight distribution of microblog $b$.
Unlike TF-IDF, Twitter-LDA first trains the overall microblogs, allocating each microblog with a \textit{tag}.
%
The structure of \textit{tag} is as follows:
\begin{equation}
\label{eq:tw-tag}
W_t = \{(w'_i, p'_i)\},
\end{equation}
where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in microblogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$ ($|W_t|\ =\ 30$ in this work by default).
%
Subsequently, $W_t$ is leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.

@@

\stitle{Step 5:} Repeat Steps 1 to 4 for the microblog $b$ over every topic in lexicon, i.e., $\forall {\gamma}_k \in L$ results one similarity value of $sim(b, {\gamma}_k)$.
Such computation further extends to all the microblogs owned by user $u$, such that:
$\forall b_m \in B_u$, $\forall {\gamma}_k \in L$, there exists a similarity of $sim(b_m, {\gamma}_k)$.
Hence, the overall similarity of user $u$ over lexicon topics $\{\gamma\}$ (i.e., $L$), written as $S(u,\ L)$, could be denoted by a vector:
\begin{equation}
\label{eq:simul}
S(u, L) = (s_0, s_1, \ldots,\ s_{n-1}),
\end{equation}
where $n$ refers to the cardinality of $L$ (i.e., number of topics in $L$) and $s_k$ is the overall similarity of user $u$ over topic ${\gamma}_k$, which is given by:
\begin{equation}
\label{eq:simul-2}
s_k = \sum_{\substack{m}} sim(b_m, {\gamma}_k).
\end{equation}

### 2018-03-02 DASFAA_2018/CR/Gruba_final/05-gm.tex

%	\stab(3) \stitle{Interaction Info} includes seven correlation metrics. They are of \#$B_u$, $R_{oc,u}$, \#$W_{r,u}$, \#$W_{t,u}$, %microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a. long-term/stable interest in this work), $b$ versus %$u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent microblogs (e.g., within 30 days) in the same manner of $P_f(u)$, %and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_{rt,u}$.
%\end{itemize}
	\stab(3) \stitle{Interaction Info} includes seven correlation metrics: \#$B_u$, $R_{oc,u}$, \#$W_{r,u}$, \#$W_{t,u}$, microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_u$ (a.k.a. long-term/stable interest in this work), and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_{rt,u}$.
%In addition, the correlation between microblog contents and $u$'s short-term interest mined from $u$'s recent microblogs (e.g., within 30 days) is also taken in consideration.
%In addition, the correlation between microblog contents and $u$'s short-term interest is also taken in consideration. The short-term %interest is expressed as
In addition, we consider $u$'s short-term interest, which is mined from $u$'s recent microblogs (e.g., within 30 days) and calculated by \textit{TF-IDF}, namely $W_s$.
The correlation between microblog and $u$'s short-term interest is computed by $W_f$ and $W_s$ (using formula \ref{eq:sim-tf1}).
%%

The modeling of retweeting behavior of groups is treated as a classification problem, and utilize the random forest classifier to address it. Details for random forest \cite{IEEEexample:conf/icdar/Ho1995} are omitted here for space reason.
The advantage of this classification model lies in that it could integrate different features conveniently, and
%The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently.
the obtained group behavior model could learn what a positive/negative item looks like over each metric mentioned above. \par
Here we use accuracy to evaluate our model. To define accuracy, we set four variables: $E_{tp}$,$E_{fp}$,$E_{tn}$ and $E_{fn}$. For a given item $E$, if $E$ is a positive item and our model also determines it a positive item, then we set $E_{tp}$ to 1, else we set $E_{tp}$ to 0. If $E$ is a negative item and our model determines it a positive item, then we set $E_{fp}$ to 1, else we set $E_{fp}$ to 0. If $E$ is a negative item and our model determines it a negative item, then we set $E_{tn}$ to 1, else we set $E_{tn}$ to 0. If $E$ is a positive item and our model determines it a negative item, then we set $E_{fn}$ to 1, else we set $E_{fn}$ to 0. So the accuracy can be defined as:

>>>>

%	\stab(3) \stitle{Interaction Info} includes seven correlation metrics. They are of \#$B_u$, $R_{oc,u}$, \#$W_{r,u}$, \#$W_{t,u}$, %microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_f(u)$ (a.k.a. long-term/stable interest in this work), $b$ versus %$u$'s short-term interest $P_s(u)$ that is mined from $u$'s recent microblogs (e.g., within 30 days) in the same manner of $P_f(u)$, %and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_{rt,u}$.
%\end{itemize}
	\stab(3) \stitle{Interaction Info} includes seven correlation metrics: \#$B_u$, $R_{oc,u}$, \#$W_{r,u}$, \#$W_{t,u}$, microblog $b$ versus the user $u$'s \textit{Interest Feature} $P_u$ (a.k.a. long-term/stable interest in this work), and $b$'s timestamp versus the time distribution of $u$'s \retg{} behavior $P_{rt,u}$.
%In addition, the correlation between microblog contents and $u$'s short-term interest mined from $u$'s recent microblogs (e.g., within 30 days) is also taken in consideration.
%In addition, the correlation between microblog contents and $u$'s short-term interest is also taken in consideration. The short-term %interest is expressed as
In addition, we consider $u$'s short-term interest, which is mined from $u$'s recent microblogs (e.g., within 30 days) and calculated by \textit{TF-IDF}, namely $W_s$.
The correlation between microblog $b$ and $u$'s short-term interest is computed by $W_f$ and $W_s$ (using formula \ref{eq:sim-tf1}).
%%

The modeling of retweeting behavior of groups is treated as a classification problem, and we utilize the random forest classifier to address it. Details for random forest \cite{IEEEexample:conf/icdar/Ho1995} are omitted here for space reason.
The advantage of this classification model lies in that it could integrate different features conveniently, and
%The advantage of using classification model is that we can integrate different combinations of the features into the model conveniently.
the obtained group behavior model could learn what a positive/negative item looks like over each metric mentioned above. \par
Here we use accuracy to evaluate our model. To define accuracy, we set four variables: $E_{tp}$,$E_{fp}$,$E_{tn}$ and $E_{fn}$. For a given item $E$, if $E$ is a positive item and our model also determines it a positive item, then we set $E_{tp}$ to 1, else we set $E_{tp}$ to 0. If $E$ is a negative item and our model determines it a positive item, then we set $E_{fp}$ to 1, else we set $E_{fp}$ to 0. If $E$ is a negative item and our model determines it a negative item, then we set $E_{tn}$ to 1, else we set $E_{tn}$ to 0. If $E$ is a positive item and our model determines it a negative item, then we set $E_{fn}$ to 1, else we set $E_{fn}$ to 0. So the accuracy can be defined as:

### 2018-03-02 DASFAA_2018/CR/Gruba_final/06-perf.tex

\stitle{Exp-2: User Clustering}
%
Fig.\ \ref{fig:10-c} depicts the Silhouette coefficient Values of multiple clustering solutions, with the cluster number varied from 2 to 10.
Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users, and each of \textit{\{Data1,\ldots, Data5\}} contains 10K randomly selected users.
Except for \textit{Data1}, solutions for \textit{\{Data2,\ldots, Data5\}} are the best for 4 clusters.

@@

\stitle{Exp-3: Behavior Modeling}
%
Fig.\ \ref{fig:10-a} shows the performance of \sys{} against the state of the art approach LRC-BQ \cite{IEEEexample:conf/ijcai/ZhangLTCL13}.
We evaluate the performance using the metrics of accuracy.
LRC-BQ does not deal with user grouping.
Hence, we not only study the modeling effect per group (i.e., ``Group-One/Two/Three/Four'' with user clustering),
but also examine \sys{} versus LRC-BQ in the case that all users are in a single group (i.e., ``All-Users'').
The results show that:
%\begin{itemize}

>>>>

\stitle{Exp-2: User Clustering}
%
Fig.\ \ref{fig:10-c} depicts the Silhouette coefficient values of multiple clustering solutions, with the cluster number varied from 2 to 10.
Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users, and each of \textit{\{Data1,\ldots, Data5\}} contains 10K randomly selected users.
Except for \textit{Data1}, solutions for \textit{\{Data2,\ldots, Data5\}} are the best for 4 clusters.

@@

\stitle{Exp-3: Behavior Modeling}
%
Fig.\ \ref{fig:10-a} shows the performance of \sys{} against the state of the art approach LRC-BQ \cite{IEEEexample:conf/ijcai/ZhangLTCL13}.
We evaluate the performance using the metrics of accuracy.
LRC-BQ does not deal with user grouping.
Hence, we not only study the modeling effectiveness per group (i.e., ``Group-One/Two/Three/Four'' with user clustering),
but also examine \sys{} versus LRC-BQ in the case that all users are in a single group (i.e., ``All-Users'').
The results show that:
%\begin{itemize}
